Adaptive Disk Storage for Interaction Graphs

### 2014-04-18 notes/graph-adapt/main.tex
block size

Let $Q$ be the query workload, where each query $q\in Q$ accesses a set of
attributes $q.A$ and traverses parts of the graph for the time range
$q.T=[q.t_s,q.t_e]$. We denote the set of all attributes as $A$. Given a block
$B$, we denote its time range as $B.T$, which is the union of the time ranges
of its temporal neighborlists. Let $s(a)$ denote the size of an attribute $a$.
We also use the same notation for block size, that is $s(B)$ for a block $B$. 
We use $c(B)$ to denote the number of entries in the temporal neighborlists
within block $B$, that is the number of edges in the block.

@@

The storage overhead can be formalized as:
\begin{equation}
H(\mathcal{P}(B)) = |\mathcal{P}(B)|\cdot\left(1-\frac{c(B)\cdot \sum_{a\in A} s(a)}{s(B)}\right) 
\end{equation}

>>>>

Let $Q$ be the query workload, where each query $q\in Q$ accesses a set of
attributes $q.A$ and traverses parts of the graph for the time range
$q.T=[q.t_s,q.t_e]$. We denote the set of all attributes as $A$. Given a block
$B$, we denote its time range as $B.T$, which is the union of the time ranges
of its temporal neighborlists. Let $s(a)$ denote the size of an attribute $a$.
We use $c_n(B)$ to denote the number of temporal neighborlists within block
$B$ and $c_e(B)$ to denote the total number of edges in the temporal
neighborlists within the block. We overload the notation for block size and
use $s(B)$ to denote the size of a block $B$. We have: 
\begin{equation}
s(B) = c_e(B) \cdot \left(16 + \sum_{a\in A} s(a)\right) + c_n(B) \cdot 12  
\end{equation}
Here, $16$ corresponds to the cost of storing the edge id and the timestamp,
and $qw$ corresponds to the cost of storing the head vertex ($8$ bytes) plus
the number of entries ($4$ bytes) for a temporal neighborlist.

@@

The storage overhead can be formalized as:
\begin{equation}
H(\mathcal{P}(B)) = |\mathcal{P}(B)|\cdot\left(1-\frac{c_e(B)\cdot \sum_{a\in A} s(a)}{s(B)}\right) 
\end{equation}
